Verification of a Deterministic Random Bits Generator

### 2015-12-23 paper/paper.tex
fixed new line formatting

\subsection{The Update Function}
Before showing any of the public function, I must first define a helper function, the \lstinline{HMAC_DRBG_Update} function,  or the \lstinline{update} function. See \stdtitle{NIST SP 800-90A \S 10.1.2.2} for the corresponding NIST specification. The \lstinline{update} function takes a \lstinline{key}, a \lstinline{value}, and an optional nonce and returns a new \lstinline{key} and a new \lstinline{value}. This function will be called at least once in each of the public functions, and the goal is to provide backtracking resistance. What this means is that the original \lstinline{key} cannot be computed from the new \lstinline{key} (note that the \lstinline{value}(s) is public anyways; see \ref{funcgenerate}).

@@

Of the actual parameters of this function (everything from and including \lstinline{entropy_stream}), \lstinline{security_strength} has already been explained. \lstinline{prediction_resistance_flag} is used to indicate whether this particular instantiation of DRBG will provide prediction resistance. \lstinline{personalization_string} is expected to be unique, and can include things like the device identifier, timestamp, etc. The idea is not to provide more randomness but to ensure that this particular instantiation will be different from any other instantiations.

@@

The \lstinline{generate} algorithm first checks if the number of times \lstinline{generate} has been called (\lstinline{reseed_counter}) is too high, and if so, returns a flag saying a reseed is needed. Otherwise, it repeatedly HMACs the current \lstinline{value} with the current \lstinline{key}, append the result to the output, and store the result as the new \lstinline{value}. This is why the \lstinline{value} part of the DRBG state is not considered secret, and is really the output of the DRBG. The output is then trimmed down to the requested number of bytes, and \lstinline{reseed_counter} is incremented by \lstinline{1}.

@@

Here, \lstinline{HMAC_Final} is the name of the \lstinline{final} function verified by previous efforts, and \lstinline{mbedtls_md_hmac_finish} is the name mbedTLS expects. The API specification (how the function interacts with local variable and memory) for this function is almost a complete copy of the specification defined by the previous HMAC verification efforts.

@@

The functions \lstinline{mbedtls_md_hmac_starts}, \lstinline{mbedtls_md_hmac_update}, and \lstinline{mbedtls_md_hmac_finish} have counterparts in the \stdtitle{OpenSSL} library, and so can just call through to them.

>>>>

\subsection{The Update Function}
Before showing any of the public function, I must first define a helper function, the \lstinline{update} function. See \stdtitle{NIST SP 800-90A \S 10.1.2.2} for the corresponding NIST specification. The \lstinline{update} function takes a \lstinline{key}, a \lstinline{value}, and an optional nonce and returns a new \lstinline{key} and a new \lstinline{value}. This function will be called at least once in each of the public functions, and the goal is to provide backtracking resistance. What this means is that the original \lstinline{key} cannot be computed from the new \lstinline{key} (note that the \lstinline{value}(s) is public anyways; see \ref{funcgenerate}).

@@

Of the actual parameters of this function (everything from and including \lstinline{entropy_stream}), \lstinline{security_strength} has already been explained. \lstinline{prediction_resistance_flag} is used to indicate whether this particular instantiation of DRBG will provide prediction resistance.\\ \lstinline{personalization_string} is expected to be unique, and can include things like the device identifier, timestamp, etc. The idea is not to provide more randomness but to ensure that this particular instantiation will be different from any other instantiations.

@@

The \lstinline{generate} algorithm first checks if the number of times \lstinline{generate} has been called\\ (\lstinline{reseed_counter}) is too high, and if so, returns a flag saying a reseed is needed. Otherwise, it repeatedly HMACs the current \lstinline{value} with the current \lstinline{key}, append the result to the output, and store the result as the new \lstinline{value}. This is why the \lstinline{value} part of the DRBG state is not considered secret, and is really the output of the DRBG. The output is then trimmed down to the requested number of bytes, and \lstinline{reseed_counter} is incremented by \lstinline{1}.

@@

Here, \lstinline{HMAC_Final} is the name of the \lstinline{final} function verified by previous efforts, and\\ \lstinline{mbedtls_md_hmac_finish} is the name mbedTLS expects. The API specification (how the function interacts with local variable and memory) for this function is almost a complete copy of the specification defined by the previous HMAC verification efforts.

@@

The functions \lstinline{mbedtls_md_hmac_starts}, \lstinline{mbedtls_md_hmac_update}, and\\ \lstinline{mbedtls_md_hmac_finish} have counterparts in the \stdtitle{OpenSSL} library, and so can just call through to them.
